---
title: "07/09/2015 Checking CAFein's input model WD:"
output: html_document
---

Here I check the c2 parameter needed by CAFein. 
I computed it in two ways: 1) via Steffen, 2) using spline in R.
```{r message=FALSE, warning = FALSE}

library(ggplot2)
library(grid)
library(gridExtra)
source("multiplot.R")

setwd("/Users/francesca/Northwestern/Research/create_models_input_CAFein/FromMESA_fixedUnitsIn_07082015")
filename = "output/WD/0p23Msun/log1673/MESAtoCAFein_log1673_0p23Msun_Z0p02_WD_deltaX5eM5in_07132015.dat"
all_content <- readLines(filename)
toSkip <- c(1, 2, 3, 4)
skipBeginning <- all_content[-toSkip]

dat <- read.table(textConnection(skipBeginning))
```

Plotting various parameters
```{r message=FALSE, warning = FALSE}

names(dat) <- c("m","logrho","logP","logT","r","Vg","Astar","U","c1","N2","L2overllp1","g","Lr","V","del_ad","del","Cp","v_t","kappa_s","eps_ad","eps_s","c2_fitted","c3","c4","dlnLr_dlnr","P_scale","StartRadSurfLayer","EndRadSurfLayer","Gamma1","entropy","kappa","chiRho","chiT","UoverUsurf","c2")

VgM3 <- dat$Vg-3

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = Vg), color = "red")+geom_line(aes(y = VgM3))+ ggtitle("Vg vs r")+ theme_bw()+scale_y_log10()
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = Vg), color = "red")+geom_line(aes(y = VgM3))+ ggtitle("Vg vs r surface close-up")+ theme_bw()+scale_y_log10()+xlim(0.999,1)+ylim(10, 1e4)
multiplot(p1, p2, cols=2)


p1 <- ggplot(dat, aes(r))+geom_line(aes(y = v_t))+ ggtitle("Vt = Cp*delAd*rho*T/P vs r")+theme_bw()+xlim(0.,1)
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = v_t))+ theme_bw()+xlim(0.98,0.999)
p3 <- ggplot(dat, aes(r))+geom_line(aes(y = v_t))+ theme_bw()+xlim(0.999,0.9995)
p4 <- ggplot(dat, aes(r))+geom_line(aes(y = v_t))+ theme_bw()+xlim(0.9995,1)+ylim(1, 2.6)

multiplot(p1, p2, p3, p4, cols=2)

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = Cp))+ theme_bw()+scale_y_log10()
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = Cp))+ theme_bw()+scale_y_log10()+xlim(0.98,0.998)#+ylim(10, 1e4)
p3 <- ggplot(dat, aes(r))+geom_line(aes(y = Cp))+ theme_bw()+scale_y_log10()+xlim(0.998,0.999)#+ylim(10, 1e4)
p4 <- ggplot(dat, aes(r))+geom_line(aes(y = Cp))+ theme_bw()+scale_y_log10()+xlim(0.999,1)#+ylim(10, 1e4)

multiplot(p1, p2, p3, p4, cols=2)

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = logrho))+ theme_bw()
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = logT))+ theme_bw()
p3 <- ggplot(dat, aes(r))+geom_line(aes(y = logP))+ theme_bw()
multiplot(p1, p2, p3, cols=1)

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = del_ad))+ theme_bw()
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = del_ad))+ theme_bw()+xlim(0.98,0.998)#+ylim(10, 1e4)
p3 <- ggplot(dat, aes(r))+geom_line(aes(y = del_ad))+ theme_bw()+xlim(0.998,0.999)#+ylim(10, 1e4)
p4 <- ggplot(dat, aes(r))+geom_line(aes(y = del_ad))+ theme_bw()+xlim(0.999,1)#+ylim(10, 1e4)

multiplot(p1, p2, p3, p4, cols=2)

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = Astar))+ theme_bw()+ylim(-50, 50)
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = Astar))+ theme_bw()+xlim(0.98,0.998)+ylim(-150, 120)
p3 <- ggplot(dat, aes(r))+geom_line(aes(y = Astar))+ theme_bw()+xlim(0.998,0.999)+ylim(-150, 120)
p4 <- ggplot(dat, aes(r))+geom_line(aes(y = Astar))+ theme_bw()+xlim(0.999,1)#+ylim(10, 1e4)

multiplot(p1, p2, p3, p4, cols=2)

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = N2))+ theme_bw()+ylim(-50, 50)
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = N2))+ theme_bw()+xlim(0.98,0.998)+ylim(-150, 120)
p3 <- ggplot(dat, aes(r))+geom_line(aes(y = N2))+ theme_bw()+xlim(0.998,0.999)+ylim(-150, 120)
p4 <- ggplot(dat, aes(r))+geom_line(aes(y = N2))+ theme_bw()+xlim(0.999,1)#+ylim(10, 1e4)

multiplot(p1, p2, p3, p4, cols=2)

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = g))+ theme_bw()#+ylim(-50, 50)
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = U))+ theme_bw()#+ylim(-50, 50) 
multiplot(p1, p2, cols=1)

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = Lr))+ theme_bw()#+ylim(-50, 50) 
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = c1))+ theme_bw()#+ylim(-50, 50) 
multiplot(p1, p2, cols=1)

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = del))+ theme_bw()+ylim(-50, 50)
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = del))+ theme_bw()+xlim(0.98,0.998)
p3 <- ggplot(dat, aes(r))+geom_line(aes(y = del))+ theme_bw()+xlim(0.998,0.999)
p4 <- ggplot(dat, aes(r))+geom_line(aes(y = del))+ theme_bw()+xlim(0.999,1)#+ylim(10, 1e4)
multiplot(p1, p2, p3, p4, cols=2)

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = c2)) + theme_bw()
p1

p1 <- ggplot(dat, aes(r))+geom_line(aes(y = c2))+geom_line(aes(y = c2_fitted), color='red')+xlim(0,0.75)+ylim(-2.5,1)+ theme_bw()
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = c2))+geom_line(aes(y = c2_fitted), color='red')+xlim(0.75,0.9)+ylim(-4,-1.4)+ theme_bw()
p3 <- ggplot(dat, aes(r))+geom_line(aes(y = c2))+geom_line(aes(y = c2_fitted), color='red')+xlim(0.9,0.99)+ylim(-50,1)+ theme_bw()
multiplot(p1, p2, p3, cols=1)
p1 <- ggplot(dat, aes(r))+geom_line(aes(y = c2))+geom_line(aes(y = c2_fitted), color='red')+xlim(0.99,0.995)+ylim(-200,0)+ theme_bw()
p2 <- ggplot(dat, aes(r))+geom_line(aes(y = c2))+geom_line(aes(y = c2_fitted), color='red')+xlim(0.995,0.999)+ylim(-1000,0)+ theme_bw()
p3 <- ggplot(dat, aes(r))+geom_line(aes(y = c2))+geom_line(aes(y = c2_fitted), color='red')+xlim(0.999,0.9997)+ylim(0,1000)+ theme_bw()
multiplot(p1, p2, p3, cols=1)
p1 <- ggplot(dat, aes(r))+geom_line(aes(y = c2))+geom_line(aes(y = c2_fitted), color='red')+xlim(0.9997,1)+ylim(-4000,4000)+ theme_bw()
p1
#p2 <- ggplot(dat, aes(r))+geom_line(aes(y = c2))+ theme_bw()+xlim(0.98,0.998)
#p3 <- ggplot(dat, aes(r))+geom_line(aes(y = c2))+ theme_bw()+xlim(0.998,0.999)
#p4 <- ggplot(dat, aes(r))+geom_line(aes(y = c2))+ theme_bw()+xlim(0.999,1)#+ylim(10, 1e4)
#multiplot(p1, p2, p3, p4, cols=2)
```
## Conclusions:

- some functions have spikes very close tot he surface, but interestingly they don't blow up (e.g., v_t reaches 2.5...)
- clearly fitting the del_ad improved c2 significantly.
- I think now we can do the following tests
1. restart CAFein as is but with the new input model
2. restart CAFein but chopping the surface
3. restart CAFein using a WD model computed with MESA latest release.
- is the spike in v_t physical?
