---
title: "07/09/2015 Smoothing out the del_ad for my WD model:"
output: html_document
---

The data file I am using has been created with MESA. 
In the region of the star where del_AD has the most variations I added data points using Steffein interpolants. 
Below I fit the data with a smooth spline.

```{r message=FALSE, warning = FALSE}

library(ggplot2)
library(grid)
library(gridExtra)

setwd("/Users/francesca/Northwestern/Research/create_models_input_CAFein/FromMESA_fixedUnitsIn_07082015")
dat <- read.table("r_delAd_Lr.dat", header =  TRUE)

plot(x = dat$r_over_R, y = dat$Lr, log = "y", xlab="r/R",ylab="Lr dimensionless", main = "Luminosity is basically zero")

dat <- dat[,1:3]
names(dat) <- c("r", "delAd", "derivDelAd")
dat$origin <- c("model")

#fitting a spline
dat.spl <- smooth.spline(dat$r, dat$delAd, spar = 0.01)

#deriving the fitted del_ad and its derivative
newR <- predict(dat.spl, dat$r, deriv = 0)$x
newDelAd <- predict(dat.spl, dat$r, deriv = 0)$y
newDerivDelAd <- predict(dat.spl, dat$r, deriv = 1)$y

derived_dat <- cbind(newR, newDelAd, newDerivDelAd)
derived_dat <- data.frame(derived_dat)
derived_dat$origin <- c("fitted")
names(derived_dat) <- names(dat)

# adding the derived values to the original data frame
# I want to compare Steffen and the spline
all_dat <- rbind(dat, derived_dat)
all_dat$origin <- as.factor(all_dat$origin)

all_dat$r <- as.numeric(all_dat$r)
all_dat$delAd <- as.numeric(all_dat$delAd)
all_dat$derivDelAd <- as.numeric(all_dat$derivDelAd)
```

#Plotting del_ad vs r for various intervals

```{r message=FALSE, warning = FALSE}

p1 <- ggplot(all_dat, aes(r, delAd, color = origin)) + geom_point()+geom_line()+xlim(0, 0.6)+ylim(0.385, 0.395)+ theme_bw()
p1
p2 <- ggplot(all_dat, aes(r, delAd, color = origin)) + geom_point()+geom_line()+xlim(0.6,0.75)+ylim(0.3925, 0.395)+ theme_bw()
p2
p3 <- ggplot(all_dat, aes(r, delAd, color = origin)) + geom_point()+geom_line()+xlim(0.75,0.85)+ylim(0.392, 0.396)+ theme_bw()
p3
p4 <- ggplot(all_dat, aes(r, delAd, color = origin)) + geom_point()+geom_line()+xlim(0.85,0.96)+ylim(0.392, 0.394)+ theme_bw()
p4
p5 <- ggplot(all_dat, aes(r, delAd, color = origin)) + geom_point()+geom_line()+xlim(0.96,0.996)+ylim(0.393, 0.394)+ theme_bw()
p5

plot(dat$r, dat$delAd, type = "o", xlim=c(0.996, 0.9992), ylim = c(0.1, 0.4))
lines(dat.spl, col="red")

plot(dat$r, dat$delAd, type = "o", xlim=c(0.9992, 1.0001), ylim = c(0.1, 0.4))
lines(dat.spl, col="red")
```

#Plotting the derivative of del_ad vs r for various intervals

```{r message=FALSE, warning = FALSE}

p1 <- ggplot(all_dat, aes(r, derivDelAd, color = origin)) + geom_point(size = 1.0)+geom_line()+xlim(0, 0.6)+ylim(-0.01, 0.025)+ theme_bw()
p1
p2 <- ggplot(all_dat, aes(r, derivDelAd, color = origin)) + geom_point(size = 1.0)+geom_line()+xlim(0.6,0.75)+ylim(-0.05, 0.025)+ theme_bw()
p2
p3 <- ggplot(all_dat, aes(r, derivDelAd, color = origin)) + geom_point(size = 1.0)+geom_line()+xlim(0.75,0.85)+ylim(-0.4, 0.2)+ theme_bw()
p3
p4 <- ggplot(all_dat, aes(r, derivDelAd, color = origin)) + geom_point(size = 1.0)+geom_line()+xlim(0.85,0.96)+ylim(-0.1, 0.1)+ theme_bw()
p4
p5 <- ggplot(all_dat, aes(r, derivDelAd, color = origin)) + geom_point(size = 1.0)+geom_line()+xlim(0.96,0.996)+ylim(-0.2, 0.1)+ theme_bw()
p5

deriv.spl <- predict(dat.spl, dat$r, deriv = 1)
plot(dat$r, dat$derivDelAd, type = "o", xlim=c(0.996, 0.9992), ylim = c(-400, 10))
lines(deriv.spl, col="red")

deriv.spl <- predict(dat.spl, dat$r, deriv = 1)
plot(dat$r, dat$derivDelAd, type = "o", xlim=c(0.9992, 1.0001), ylim = c(-2000, 2000))
lines(deriv.spl, col="red")
```

Writing everything in output
```{r}

filename ="r_delAd_postRprocessing.dat"
head(derived_dat)
str(derived_dat)

options(digits=15)
write.table(format(derived_dat[,-4], scientific = TRUE), file=filename, quote = F)
```

Note, I should end the star at about 0.9999
